\documentclass[11pt]{article}

\begin{document}
Josh Muszka
% London, ON N5W 2J1 | jmuszka@uwo.ca | (519) 630-4852 | github.com/jmuszka | www.jmuszka.com | linkedin.com/in/jmuszka
---

[date]

[recruiter position]
[company]
[company location]

Dear [recruiter],

As a third year, high-achieving Computer Science student with years of programming and technical experience, I would love to contribute to [company]'s software development through the internship program. Through [source of application], I saw the opportunity to apply for [honorable description of the company].

Having real-world experience with many different technologies including [relevant languages] and [relevant frameworks], I am eager to learn new tools that will allow me to make on impact on your team and broaden my experience as a developer. Additionally, My professional roles coupled with my involvement with the campus community has cultivated my skills for clear communication and effect collaboration.

My strong academic performance in Computer Science and Mathematics demonstrates my critical thinking skills fit to solve complex challenges. Along with fundamental skills for software development, I have acquired various technological skills including databases and SQL, front and back-end architecture, operating systems, and artificial intelligence. Moreover, I have developed a solid foundation in data analytics knowledge through my courses in machine learning, statistics, and data science.

I have always admired [company]'s technology. [relate to how I've used their product(s)], what stoof out to me was [something the company has achieved]. This experience I have had with [company] has brought my interest to the software aspect. I am eager to make an impact on [company]'s technological advancement as a hard-working intern.

Thank you for your time and consideration. My dedication to software engineering and the skills to support this passion would make me a valuable asset to the [company] team. I can easily be reached by email or phone at your convenience.

Sincerely,

Josh Muszka
\end{document}